---
title: "Nicfall_Originalhwcode_01"
author: "Nicola Kriefall"
date: "9/12/2019"
output: html_document
---

# Module 04

Homework for week 2 of AN597

## Preliminaries

<i>i.e.</i> installing packages

```{r}
#install.packages("stringr") #installing required package, remove # if you don't have this package installed yet
library("stringr") #loading required package
```

## Challenge 1

First, create a vector of 1 word character strings comprising the first line of the novel Ulysses, by James Joyce: “Stately, plump Buck Mulligan came from the stairhead, bearing a bowl of lather on which a mirror and a razor lay crossed.”

```{r}
ulysses <- c("Stately, plump Buck Mulligan came from the stairhead, bearing a bowl of lather on which a mirror and a razor lay crossed.")
u_split <- str_split(ulysses,pattern=" ",simplify=TRUE)
u_split
```

Then, extract every third element of this vector.

```{r}
u2 = u_split[, seq(3, ncol(u_split), 3)]
u2
```

# Challenge 2

Given the matrix, m, below, extract the 2nd, 3rd, and 6th columns and assign them to the variable x

```{r}
m <- matrix(data=1:80,nrow=8,ncol=10,byrow=FALSE)
m
x <- m[,c(2,3,6)]
x
```